### 2014-08-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor formatting edits

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1 3/4'' hoseline.                                             \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
               &  over the next two minutes.                                                          \\
               &                                                                                      \\
10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                 &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                           &  9~min                                        &  --                                \\
Grid Cell Size                            &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                   &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fire}            \\
                                          &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                          &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                          &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fire}            \\
                                          &  Basement flashover fire: 15~MW               &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}  &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                          &  $\rho$: 810~kg/m$^3$                         &                                    \\
                                          &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}                  &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

@@

               &              &  makes entry into the front door with a 1 3/4'' hoseline.          \\

>>>>

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1~\sfrac{3}{4}~in hoseline.                                   \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
               &  over the next two minutes.                                                          \\
               &                                                                                      \\
10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                 &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                           &  9~min                                        &  --                                \\
Grid Cell Size                            &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                   &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fire}            \\
                                          &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                          &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                          &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fire}            \\
                                          &  Basement flashover fire: 15~MW               &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}  &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                          &  $\rho$: 810~kg/m$^3$                         &                                    \\
                                          &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}                  &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

@@

               &              &  makes entry into the front door with a 1~\sfrac{3}{4}~in hoseline.  \\
